Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-04-21 review_response/review_response.tex

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence 
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/) 
%
% BASIC INSTRUCTIONS: 
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,11pt]{reviewresponse}
\input{review_response_setting}

\begin{document}

\thispagestyle{plain}

\begin{center}
	{\Large\myTitle} \vspace{0.5cm} \\
%	{\large\myJournal} \vspace{0.5cm} \\
	\today \vspace{0.5cm} \\
	\myAuthors \\
	\url{\myEmail} \vspace{1cm} \\
	\myDept
\end{center}

\tableofcontents

\begin{abstract}
	We thank the anonymous reviewers for their comments.
    These comments are very useful for us to improve our paper. 
    Below, we address every comment carefully and 
    explain the corresponding changes in the manuscript.
\end{abstract}

\section{Reviewer 1}

\rcommentnoskip{
The paper describes an interpretation of the area aggregation problem as the computation of a shortest path in a suitably defined graph.
The contents of the paper are an interesting read and certainly well within the scope of TSAS.

Though I have some comments/questions about certain parts (see below), the paper is of good quality already and warrants (eventual) acceptance.         
}

\textbf{Response} Thanks for the positive comments.

\rcomment{
Problem complexity. Though the exponential lower bound works, the given example seems excessively degenerate. It works only by assuming that all rectangles have identical area---otherwise, the ``smallest area must aggregate'' severely limits the options. Can the construction be altered to show an exponential lower bound where all regions have unique sizes? (or under some other assumption that is more realistic).

Complementing this paragraph, I'm also wondering if anything is known about whether the specific problem considered here is NP-hard?  
}

\textbf{Response}
We have improved our proof of the exponential lower bound.
In the new proof, all the rectangles have unique sizes;
see Section 3.3 (Exponential Lower Bound).
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

\rcomment{
Compactness. 
Two models for compactness are given, one being linear and the other not. 
The motivation for needing the linear model is clear, 
but how different are these models? 
Is there any literature that already describes the correlation between these? 
Otherwise, I feel that the paper could be enriched 
by considering the correlation between the two in this setting 
(how well does \Astar-$g_2$ perform in terms of \Astar-$g_1$ / 
does it give similar quality when measuring $g_2$-results using $g_1$, 
or something like that). 
(Assuming you have the data/solutions, this would be comparatively easy to do?)
}

\textbf{Response} 
To the best of our knowledge, 
there is no literature describing 
the correlation between the two models for compactness.
\textcite{Li2013Compactness} reviewed some measures for compactness.

This comment will lead to an interesting research.
Of course, it is easy to compute the~$g_1$ value of the result of~\Astar-$g_2$,
and vice versa, since we have the data.
If we present the values, then it would be better to also theoretically analyze the correlation between the two compactness formulas,
which could lead to a new paper.
We may perform this research in our future work.

\rcomment{
Greedy algorithm. 
I'm missing some motivation in the paper for the given greedy choice. 
Specifically, why was this method chosen over other clear candidates? 
(e.g., always ensuring the smallest region is recolored, 
regardless of what the target eventually is?). 
Fig 18. describes a ``bad choice'' for the given greedy strategy, 
but I see no motivation/example of why it would be a good choice.
}

\textbf{Response} We have a start map and a goal map.
Our greedy algorithm must ensure that 
our final result (e.g., the polygon of layer $L_4$ in
Figure 3) will have the type of $T_\mathrm{goal}$.
This is why we should not always recolor the smallest region.
We have added this argument in Section 6 (A Greedy Algorithm).

We use a start map and a goal map because 
our aggregation sequence should be able to 
benefit from a goal map with high quality.
We have added this argument 
in ``Problem definition'' of Section 1 (Introduction).

We have added more details 
into the caption of Fig 18 (Fig 17 in the new version).

\rcomment{
Though I would rate the organization as ``acceptable'', there are many parts where I feel the presentation can be streamlined. Some points of attention:

The contributions only appear on page 5. Much of the text before is ``related work'', but much of it is only tangentially related (e.g. the apparent need to defend optimization approaches)

The problem definition is partially in the preliminaries and in the introduction (though the paragraph ``problem definition'' in the introduction seems to only partially define that problem and then continue with related work).

(Partial) suggestion: restructure such that problem definition and contributions come before ``optimization in map generalization'' and structure the paragraphs of ``optimization in...'' as related work). 
}

\textbf{Response}
We have put ``Problem definition'' and ``Contribution'' 
into Section 1 (Introduction).
We have made an individual section for related work;
see Section 2 (Related Work).

\rcomment{
Personally, I found there to be little value in the 2-page explanation on what linear programming is. It seems out of place to me, and a good place to streamline(/shorten) the exposition.

Variables, objective function and constraints are explained in separate paragraphs. I'm wondering if there is a different organization possible that requires less of the ``recall that ...'' phrasing. For example, some of the basic constraints that relate the meaning of the various variables could just be given immediately.

But that will allow integration of considerations and solutions. For example, when reading the definition of~$c_{t,p,o,r}$, I immediate wonder why that variable helps to solve connectivity (why can't two neighboring areas identify each other as the neighbor...)

It is a style-preference I suppose, but I'd rather have the ILP be built up of variables+constraints+explanation of the various smaller parts, rather than having all the variables up front (and needing to recall).

Also, something that would help a lot here is to use more meaningful variable names (instead of $x,y,z, \ldots$), such that it is easier to remember what's what.

}

\textbf{Response}
Some researchers from Geographic Information Science 
may not be familiar with integer linear programming.
Therefore, we use the coffee example to illustrate the ideas of LP and ILP.
We have put the method of using integer linear programming into Appendix.

We think it is easier for readers 
to find the definitions of variables, objectives, and constraints
if we present them in separate paragraphs.
If we mix the definitions, readers may need to search for a specific definition 
in more paragraphs as some constraints consist of two kinds of variables.

We would also like to use more meaningful variable names, 
but we do not have a good idea to do so as our variables are quite complex.

\rcomment{
With the experimental results, many of the figures and tables are far away from their referencing text. I would suggest introducing some clearpage commands to get them closer to each other, and(/or) adding some more detail to the captions to explain the main observations in the caption as well.
}

\textbf{Response} We have added a clearpage before 
Section 9.2 (Using costs of type change and length).
We have added some details to the captions of 
Figure 17, Figure 23, and Table 1 (see the new version of our paper).

\rcomment{
Introduction: to what degree is continuous generalization, 
in terms of having no discrete changes, 
possible / desirable / realistic?
}

\textbf{Response} We believe that continuous generalization is possible,
desirable, and realistic. 
We have added more arguments in Section 1 (Introduction).

\rcomment{Fig. 5 (and associated text) describes four alternative aggregation preferences. It seems that (unless degenerate) options (b) and (c, d, e) cannot be applicable simultaneously.
}

\textbf{Response} Figure 5 shows some ideas of \textcite{Cheng2006}.
It is fine options (b) and (c, d, e) cannot be applicable simultaneously.
We present this figure to show some inspirations that we got from reading the paper.
We have added the reference of \textcite{Cheng2006} into the caption.

\rcomment{Section 3.1. Is there a specific reason why the metric considers only the change between two levels? It seems that, unless the resulting patch is immediately part of another aggregation, the choice made has a longer lasting effect. In other words, in all subsequent maps, the choice causes some ``error'' in the intermediate map, yet this is only measured once.
}

\textbf{Response}
A reason is that we want to make the changes small 
so that users can follow maps easily.
We have added this argument in Section 1 (Introduction).

\rcomment{Fig. 24 -- the problem is attributed to the small shared boundary. But is this not ``simply'' an issue of compactness? (That is, the compactness is not weighted heavily enough / or not captured adequately?).
}
\textbf{Response} This is a good point of view.
In order to make the reason clear, we will need to do more experiments.
That can be our future work.

\rcomment{Can this approach also work if no target map is not given (or has no predefined type)?
}

\textbf{Response} No, we need a target map in order to use the \Astar algorithm,
which finds a shortest path from a start to a target.
However, if there is no target map, we can always generate one 
by an existing algorithm \parencite[e.g.][]{HaunertWolff2010AreaAgg};
see Section 1.

\rcomment{p2: "at any different scales" \\
p3: "as good as" -> "as well as" \\
p3: "He repeatedly displace the line until finding..." -> 
displaced/displaces \& until a ... is found  \\
p4: "based on constr. DT" -> "based on a constr. DT" or 
"based on constr. DTs". \\
p8: "by human being" -> "by a human being" \\
p32: should the equation here not have $p$ and $q$ swapped on one of the sides? \\
}

\textbf{Response} We have improved our paper according to all the six comments.

\clearpage

\section{Reviewer 2}

\rcommentnoskip{
This paper introduces a problem of continuous map generalization in which a set of polygons (referred to as the start map) is sequentially merged into a smaller set of polygons (referred to as the goal map) and compare different approaches in terms of effectiveness and efficiency. Any aggregation sequence must satisfy specific constraints, and of all such sequences, one that minimizes a specific objective function is considered as optimal.

The paper is well written, but there may be some issues to be addressed before it is further considered for publication.

In particular, the importance of the problem is questionable. The problem relies on the following assumptions: 1) The start map and the goal map consist of polygons each of which belongs to a given land-cover type. 2) Every polygon on the goal map is the union of a set of polygons on the start map. The first assumption is fine, but the second assumption considerably limits the problem’s applicability. It seems to me that the problem is interesting if the two maps come from different sources. If the goal map has been derived from the start map, the problem won’t be too different from other problems of continuous map generalization available in the literature.
}

\textbf{Response}
Even if the goal map has been derived from the start map,
the problem is still difficult if we want to have an optimal aggregation sequence.
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).
No literature has tried to solve this problem.

\rcomment{In ``A model could be to minimize the smallest change over all the steps'' (page 3) doesn't sound right. Do you mean to minimize ``greatest'' change? I may overlook something, though.
}

\textbf{Response} We indeed meant that 
an idea could be to minimize the ``smallest'' change
because we wanted to show that ideas could be bad.
However, in the new version of our paper, we changed ``smallest''
to ``greatest'' because using ``smallest'' sounds too stupid.

\rcomment{
The detailed introduction of ``Integer Linear Programming'' (with a coffee example) is not necessary.
}

\textbf{Response}
Some researchers from Geographic Information Science 
may not be familiar with integer linear programming.
Therefore, we use the coffee example to illustrate the ideas of LP and ILP.
We have put the method of using integer linear programming into Appendix.

\rcomment{The discussion on the relevance of compactness to the problem is weak. Should we impose the compactness criterion on all polygons? Some landscape features may inherently take linear forms, e.g., corridors. Does the measurement presented in Sec. 3.2 take into account the irregularity of polygons’ shapes (especially on the start map)? Is it possible (or likely or unlikely) that a non-compact polygon to be aggregated causes any bias in the aggregation sequence? 
}

\textbf{Response}
Indeed, our method will be more reasonable 
by taking into account irregular shapes.
This extension can be a future work of our paper.
In Section 10 (Concluding Remarks),
we have added
``In our setting, we ignored the fact that
some features may inherently take linear forms
(e.g., rivers)''.

\clearpage

\section{Reviewer 3}

\rcommentnoskip{

The introduction is very clear, and motivates the reader to read further.

I'm usually not a fan of having the related work woven into the introduction, but in this case, the presentation remains clear, the proposed problem is well-defined, and the contributions are delineated from the related work. In particular, the examples of Figure 1 and Figure 2 take the reader by the hand to help them understand the problem. Specifically, the authors nicely clarify that both the ``start map'' and the ``goal map'' are BOTH input parameters.

This clarifies that the goal of this paper is not to find a good generalized map, but rather, how to smoothly generate it.

Overall, the introduction is a pleasure to read. 
}

\textbf{Response} We have put the related work in an individual section;
see Section 2 (Related Work).

\rcomment{Major Revision 1:

Your model is clear and well-described. The presented subdivision graph is clearly understood.

I understand that you are using shortest-path algorithms such as A* on this graph. However, this graph is a directed acyclic graph (DAG), for which more efficient solutions for shortest-path search are known, such as ones based on topological sorting. It appears to me, that the DAG property of the subdivision graph can be exploited to achieve higher efficiency.

Baseline algorithms used for the experimental evaluation should include shortest path algorithms which are designed for DAGs.
}

\textbf{Response} We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

An off-the-shelf shortest-path algorithm for directed acyclic graphs
(e.g., \textcite[\sect25.2]{Cormen2009})
will explore the whole graph, which has exponential size.
Therefore, it is almost impossible to use a DAG-based algorithm
for our problem.
We have added this argument in Section 3.4 (Methods).

\rcomment{Major Revision 2:

The exponential lower bound in Section 2  appears to be wrong. It shows that your solution has an exponential lower bound, but it does not show that the problem has an exponential lower bound.

This is similar to the problem of sorting at array of~$n$ numerical values: There is an exponential number ($n!$) of possible intermediate steps. Any approach that enumerates all of these $n!$ possible orderings is exponential. Yet, the problem of sorting an array is not exponential.

The same appears to apply here: Would it be possible to simply aggregate the smallest region in each step, yielding a total run-time of $n$?

Would that solution be optimal? That would depend on your cost function, which is not yet defined in this part of the paper.

But in the preliminaries, you state that: ``To find a sequence of small changes that transforms the start map into the goal map, we require that every change involves only two areas of the current map. More precisely, in each step the smallest area~$u$ is merged with one of its neighbors (adjacent areas) $v$ such that~$u$ and~$v$ are replaced by their union.''

This implies that a greedy approach that always takes the smallest values would be optimal, thus leading to the ``merge-sort'' like approach sketched earlier in the paper.

Your proof of an exponential lower bound must show, not only that there exists and exponential number of states, but that any correct algorithm must explore an exponential number of states in the worst-case. Or, in other words, in the worst-case, an exponential number of nodes cannot be pruned. 
But if the task is simply to merge the smallest area with the smallest adjacent areas, then only one option remains unpruned in each step, yielding linear run-time.

Note that I am not saying that the problem is not exponentially hard for certain cost functions. But you need to clarify, for the cost function that you propose, whether the problem is exponentially hard, and how greedy and dynamic programming algorithms can not possibly find the correct answer, efficiently.
}

\textbf{Response}
We have improved our illustration of exponential lower bound;
see Section 3.3 (Exponential Lower Bound).
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

\rcomment{

I'm confused about the combination of cost functions. You propose three different cost functions, based on type ($g_\mathrm{type}$), based on compactness ($g_\mathrm{comp}$), and based on length ($g_\mathrm{lgth}$). However, in Section 3.4., you only ``combine the two cost functions''.

Why not combine all three? Why is the third defined? Why are there two combinations using two different two-subsets of cost functions?
}

\textbf{Response}
As illustrated in Section~4 (Cost Functions),
our cost function takes two aspects into account: 
one based on semantics and the other based on shape.
This is why we define~$g_\mathrm{type}$ and~$g_\mathrm{comp}$.
We also want to compare the \Astar and a method based on integer linear programming
in solving our problem, while $g_\mathrm{comp}$ cannot be computed linearly.
So we combine~$g_\mathrm{type}$ and~$g_\mathrm{lgth}$ when we make the comparison.
We have made this more clearly in Section~4.4 (Combining Cost Functions).

\rcomment{
Major Revision 3:

Section 4 is incomplete. This section defines a first part of a greedy baseline algorithm, and defines two cost functions. However, it is not clear how a greedy algorithm would utilize these cost functions.

A greedy algorithm should simply choose the patch which minimizes 
$argmax_\mathrm{candidate~patches}$ CostFunctionDefeindInSection3.

The authors need to properly define the Greedy algorithm. Reading the experiments, I'm merely assuming that the greedy algorithm does what I expect it to do (see above).
}

\textbf{Response} We have improved the section,
which becomes Section 6 (A Greedy Algorithm) in the new version of our paper.

\rcomment{
Very Major Problem 1:

The proposed Integer Linear Programming algorithm does not have convincing results. It only terminates for goal polygons having a trivially small number of sub-polygons. Even in the cases where it terminates, the result is worse than A*, and not significantly better than the naive greedy.

Due to these terrible results, I feel that there is not much intellectual merit in this approach. I suggest that authors remove details of this approach, almost entirely. The authors could still use this approach as a competitor (explained in one paragraph) in the experiments. But as a main contribution, this approach fails to deliver any meaningful results.

Instead, the authors may try different approaches that exploit that the subdivision graph is a DAG. Exploiting this property may allow significant improvement over A*.
}

\textbf{Response}
We have put the method of using integer linear programming into Appendix.

We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

An off-the-shelf shortest-path algorithm for directed acyclic graphs
(e.g., \textcite[\sect25.2]{Cormen2009})
will explore the whole graph, which has exponential size.
Therefore, it is almost impossible to use a DAG-based algorithm
for our problem.
We have added this argument in Section 3.4 (Methods).

\rcomment{Minor comments:

Page 6 Line 45: ``The patch also has the property type''. 
Please clarify what this means. I am assuming, that you want to say that each patch also has a unique land-cover area type.
In Equation 1: Region~$R$ is undefined? Should it be~$v$ instead of~$R$?

I cannot understand the idea of Figure 9. It appears that Figure 9a is not a valid partitioning.
}

\textbf{Response} According to your suggestion, 
we changed ``The patch also has the property type''
to ``Each patch also has a unique land-cover type''.
In the new version, we define region~$R$ in Section 3 (Preliminaries).

Figure 9a is not a valid partition, but it is fine for estimation.
In the new version of our paper, we add a reference to Section 7.1.

\rcomment{To summarize:

I like the problem defined in this paper, and I like the motivation and presentation. However, the main approach presented in this work (using Linear Programming) does not yield any useful theoretic or experimental results. Thus, the intellectual merit of this approach is highly questionable.

### 2019-04-24 area_agg_seq_tsas.tex
improved our paper and response according to Jan's comments

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes features in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.
We believe that digital maps will eventually 
achieve smooth changes for zooming.
A simple way is to fade in and fade out raster maps
as did by \textcite{Pantazis2009b}.
However, we would like to carry out the changes in a more elegant way;
we would like to change map features gradually.

@@

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence land-cover maps.

@@

\mypar{Contribution}
We show related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we formally model our problem, 
analyze the size of our model in a worst-case scenario,
introduce our methods,
and present the basic concepts of our method
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the concluding remarks, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

@@

We wish to maximize the sum of the average compactnesses 
over all intermediate maps,
while our objective will be
minimizing a cost function.
To adapt the average compactness to our methods, 
we define and minimize a cost related to compactness.
Recalling that there are~$n-s+1$ patches at time~$s$,
we define the cost of compactness for subdivision~\Psnode as
\begin{equation}
\label{eq:f_comp}
f_{\mathrm{comp}}(\Psnode)=
\frac{1-\frac{1}{n-s+1} \sum_{c\in C(\Psnode)}c}{n-2},
\end{equation}
where we use values~$n-s+1$ and~$n-2$ to normalize 
the cost of compactness.

@@

We denote the set of interior boundaries 
for a subdivision~$\Psnode$ by~$B(\Psnode)$.
The cost in terms of interior length of 
this subdivision is defined as
\begin{equation}
\label{eq:f_length}
f_{\mathrm{lgth}}(\Psnode)=
\frac{\big(\sum_{b\in B (\Psnode)} 
	|b|\big)\big/D(s)}{n-2}, 
\end{equation} 
where 
\begin{equation}
\label{eq:AreaAgg_Norm}
D(s)=\frac{n-s}{n-1} \sum_{b\in B (\Pstart)} |b|.
\end{equation}
Function~$D(s)$ computes the ``expected'' total length of 
the interior boundaries at time~$s$,
where we expect that this total length decreases linearly
according to time~$s$.
In special,~$D(1) = \sum_{b\in B (\Pstart)} |b|$
and~$D(n) = 0$.
Similarly to \eq\ref{eq:f_comp}, 
we use~$D(s)$ and~$n-2$ to normalize 
the cost of length.

@@

@@

>>>>

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polyglines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

We consider CMG as the process of producing maps 
covering a continuous interval of scales,
where CMG considers constraints and quality measures 
that act across different scales. 
In our work, for example, the quality of an aggregation sequence 
is measured as a whole; 
whereas in classical generalization approaches, 
only the quality of a map at some output scale is measured.
We consider CMG possible, desirable, and realistic.
In CMG, it is not necessary that 
all changes that occur during zooming are animated in a continuous fashion. 
That fashion may generally be possible. 
A simple way is to fade in and fade out raster maps
as did by \textcite{Pantazis2009b}, 
but it is not at all clear 
whether such animations would improve the experience of the map user.
By contrast, we would like to carry out the changes in a more elegant way;
we would like to change map features gradually.

@@

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Note that although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence land-cover maps.

Our method can also be extended to find an aggregation sequence 
for two maps (a start map and a goal map) that are from different sources.
In that case, one could compute a map overlay of the two maps
and use the result 
(with combined boundaries from both input maps and land cover classes 
from the given large-scale map) 
as the start map.

@@

\mypar{Contribution}
We show related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we formally model our problem, 
analyze the size of our model in a worst-case scenario,
introduce our methods,
and present the basic concepts of our method
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether \Astar or the ILP-based algorithm, 
which are more complex and slower, indeed perform better.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the concluding remarks, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

@@

We wish to maximize the sum of the average compactnesses 
over all intermediate maps,
while our objective will be
minimizing a cost function.
To adapt the average compactness to our methods, 
we define and minimize a cost related to compactness.
Recalling that there are~$n-s+1$ patches at time~$s$,
we define the cost of compactness for subdivision~\Psnode as
\begin{equation}
\label{eq:f_comp}
f_\mathrm{comp}(\Psnode)=
\frac{1-\frac{1}{n-s+1} \sum_{c\in C(\Psnode)}c}{n-2},
\end{equation}
where we use values~$n-s+1$ and~$n-2$ to normalize 
the cost of compactness.

@@

We denote the set of interior boundaries 
for a subdivision~$\Psnode$ by~$B(\Psnode)$.
The cost in terms of interior length of 
this subdivision is defined as
\begin{equation}
\label{eq:f_length}
f_\mathrm{lgth}(\Psnode)=
\frac{\big(\sum_{b\in B (\Psnode)} 
	|b|\big)\big/D(s)}{n-2}, 
\end{equation} 
where 
\begin{equation}
\label{eq:AreaAgg_Norm}
D(s)=\frac{n-s}{n-1} \sum_{b\in B (\Pstart)} |b|.
\end{equation}
Function~$D(s)$ computes the ``expected'' total length of 
the interior boundaries at time~$s$,
where we expect that this total length decreases linearly
according to time~$s$.
In special,~$D(1) = \sum_{b\in B (\Pstart)} |b|$
and~$D(n) = 0$.
Similarly to \eq\ref{eq:f_comp}, 
we use~$D(s)$ and~$n-2$ to normalize 
the cost of length.

@@

Note that in theory, a patch, $u$, with a small perimeter 
can be extremely non-compact 
according to measure~$c(u)$ in \eq\ref{eq:comp}, 
thus the two measures, $f_\mathrm{comp}$ and~$f_\mathrm{lgth}$, 
are not interchangeable. 
However, if we assume that all areas of the map have the same size 
(i.e., $A_u$ of \eq\ref{eq:comp} is a constant), 
it would make no difference whether 
we minimize an area's perimeter 
or maximize the area's compactness~$c(u)$. 
Obviously, the areas in our dataset have different sizes. 
However, since we iteratively remove the smallest area, 
the differences do not become too large. 
Therefore, measuring the overall compactness of a map 
based on the total length of all the interior boundaries is quite reasonable.

@@

A motivation for the greedy algorithm is that 
a very similar iterative algorithm has been used by
\textcite{vanOosterom1995Development} 
for constructing the tGAP data structure.
However, we have to make minor modifications to ensure that 
the computed aggregation sequence ends with the goal map that, 
in our situation, is given as a part of the input.
We use our greedy algorithm as a benchmark
so that we are able to see 
whether the \Astar algorithm or the ILP-based algorithm 
indeed perform better.
